AA Distributed Software Development Methodology

### 2013-06-02 paper.tex
integrado com hybrid

%% brief introduction
In a scenario where Global Software Development is growing as a popular 
software development scenario both for free software projects and for the entire
software industry, we need methodologies to deal with its potential disadvantages and at
the same time to amplify its advantages.

This paper has presented a methodology for GSD, \ie, the development
involving a series of large or small groups of software developers, each either working on
different countries or at the same room. The AA methodology
implements a simple system where each developer take notes of his work
posting a periodic log of small text sentences or microblogs. The sum of those
micrologs, along with an entire session of work, results in a complete
report. The report is made public available through a Website and be
validated by other developers randomly sorted by the AA Web server.

AA is not limited to a merely work-management tool, but acts as \emph{a
methodology to improve the time sensibility of individuals}, dividing their
complex work on small chunks or sessions, and also reducing the need of extensive
reports or unnecessary meetings. By asking users to write a minimal
text sentence as a continuous log feed, the proposed methodology avoids
disturbing the flow of developers which are heavily concentrated on programming: developers
just have to type a few words and go back to coding.

The AA methodology is not restricted to software development, even though it was
designed for the latter. As of this
writing there is an entertainment studio, Pula Pirata\footnote{
\url{www.pulapirata.com}}, that has started to use AA to manage their creative activities.
Other people with no software background, like social scientists, musicians and
activists also have been using AA and contributing for its improvement.

For developer teams, we have analyzed data and gained practical experience on
the use of AA to auto-regulate the work of Lab Macambira, a group of free
software developers from Brazil. Since July of 2011 the group has contributed
and created new free and open source software for a vast number of additional applications.

There are many aspects of the work which remain unfinished. Additional
ubiquitous client
interfaces for micrologging -- the `Twitter-like' messages -- from different
interfaces beyond IRC, \eg, web social services and email, would greatly make the use of
AA easier and more widespread, turning AA a truly ubiquitous and replicable system, presented on everyday
communication channels. Another research direction is that the actual work logs
generated by the Lab Macambira and Pula Pirata collectives since July of 2011
could be vastly statistically analyzed aiming to recognize patterns in the
behavior of individuals and their creative production process.

\section*{Acknowledgments}
%TODO The authors would like to thank NSF and CNPq.

We would like to thank AA: the present research and even this
manuscript was written using AA. The complete log is on-line at
\url{www.pulapirata.com/skills/aa}.

>>>>

%% brief introduction
In a scenario where Global Software Development is growing as a popular form of
software development in the entire software industry, there is an increasing
need for methodologies to deal with its potential disadvantages and at the same
time to amplify its advantages.

This paper has presented a new methodology for GSD, in scenarios
involving a series of large or small groups of software developers, either working on
different countries or at the same room. The AA methodology
implements a simple system where each developer take notes of his work
posting a periodic log of small text sentences or micrologs. The sum of those
activity logs, along with an entire session of work, results in a complete
unit of report. The report is made public available through a Website and is
validated by peers that are randomly selected by the AA Web server.

AA is not limited to a work-management tool, but acts as \emph{a
methodology to improve the time sensibility of individuals}, helping divide their
complex tasks in time into small chunks or sessions, and also reducing the need
of extensive reports or unnecessary meetings. By asking users to write a minimal
text sentence as a continuous log feed, the proposed methodology avoids
disturbing the flow of developers which are heavily concentrated on programming:
developers just have to type a few words and go back to coding.

We have analyzed data and gained practical experience on
the use of AA to auto-regulate the work of Lab Macambira, a group of free
software developers from Brazil. Since July of 2011 the group has contributed
and created new free and open source software for a vast number of additional applications.

The AA methodology is not restricted to software development, even though it was
designed for the latter. As of this writing there is an entertainment studio,
Pula Pirata\footnote{ \url{www.pulapirata.com}}, that has been using AA to
manage their creative activities.  Other people with no software background,
like social scientists, musicians and activists also have been using AA and
contributing for its broader improvement.

There are many aspects of the work which remain unfinished. Additional
ubiquitous client interfaces for micrologging from different interfaces beyond
IRC, \eg, web social services and email, would greatly make the use of AA easier
and more widespread, turning AA a truly ubiquitous and replicable system,
presented on everyday communication channels. Another research direction is that
the actual work logs generated by the Lab Macambira and Pula Pirata collectives
since July of 2011 could be statistically analyzed aiming to recognize
patterns in the behavior of individuals and their creative production process.
It would also be desirable to provide more extensive experiments and
psychological studies focusing on further backing specific claims made in this
paper, in order to refine the methodology, its mechanisms and parameters.

\section*{Acknowledgments}
The authors acknowledge the financial support from Pontao Nos Digitais, and
Ricardo Fabbri acknowledges support from FAPERJ/Brazil 111.852/2012.
We would also like to thank AA: the present research and even this
manuscript was written using AA. The complete log is on-line at
\url{www.pulapirata.com/skills/aa}.
